\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{setspace}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\columnsep}{2in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}{\textwidth}{{\extracolsep{\fill}}}
  \textbf{{\huge Nishanth Solomon}}\\
  \href{nishanthsolomon.github.io}{nishanthsolomon.github.io} | {nsolomo2@asu.edu} | {+1(480)930-2842} | \href{https://linkedin.com/in/nishanthsolomon/}{linkedin.com/in/nishanthsolomon}
    % \begin{multicols}{3}
    %     \href{nishanthsolomon.github.io}{nishanthsolomon.github.io}
    %     \columnbreak
    %     {nsolomo2@asu.edu}
    %     \columnbreak
    %     {+1(480)930-2842}
    % \end{multicols}
\end{center}




%-----------EXPERIENCE-----------------
\section{Summary}
{Graduate student and versatile programmer with 2+ years of research in Natural Language Processing, Deep Learning, and work experience in end-to-end Development and Deployment of Software as a Service(SaaS) and seeking a full-time position as a software developer starting in May 2021.}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Science in Robotics and Autonomous Systems}{\textit{August 2019 - May 2021}}
      {Arizona State University, Tempe, USA}{3.89/4}
    \resumeSubheading
      {Bachelor of Engineering in Mechanical}{\textit{July 2013 - May, 2017}}
      {Anna University, Chennai, India}{8.11/10.0}
  \resumeSubHeadingListEnd

% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   {
     \textbf{Databases}{: PostgreSQL, MySQL}
     \newline
     \textbf{Deep Learning Libraries}{: AllenNLP, PyTorch, NLTK, spaCy, Scikit-Learn}
     \newline
     \textbf{Programming Languages}{: Python, Java, JavaScript, Matlab, C, C++}
     \newline
     \textbf{Version Control System}{: Git (GitHub, GitLab)}
     \newline
     \textbf{Web Frameworks}{: Cherrypy, Flask}
   }
 \resumeSubHeadingListEnd
 
%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{\textit{May 2017 - July 2019}}
      {Zoho Corporation}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Natural Language Processing}
        {Built, trained and deployed Neural Networks}
        \newline{* Built a model on AllenNLP to classify an industry by feeding a TF-IDF of keywords to a three hidden layer neural network. It was able to accurately predict 45 business labels with 91\% accuracy.}
        \newline{* Developed a bi-directional LSTM with Attention Named Entity Recognition system, which located and classified named entity mentions in unstructured text into 108 pre-defined categories with sub-types.}
        \newline{* Trained a single layer Neural Network model using a bag of N-gram features, which detected the language of the given text. Reduced the model size by weight quantization and feature selection.}
        \resumeItem{DevOps}
        {Responsible for deploying and scaling REST APIs and maintaining servers in 4+ data centers.}
        \newline{* Designed, developed, tested and deployed REST APIs to expose the trained NLP models as micro-services.}
        \newline{* Configured and maintained PostgreSQL, designed and developed table models, and formulated access APIs.}
        \newline{* Managed GitLab repositories and permissions and created a chatbot with webhooks to keep the team updated.}
      \resumeItemListEnd
%     \resumeSubheading
%       {Internship}{}
%       {Zoho Corporation, Chennai, India}{Jan 2017 - Mar 2017}
% %       \small{\textit{Project Trainee}}\hspace{13cm}\small{\textit{Jan 2017 - Mar 2017}}
%       \resumeItemListStart
%         \resumeItem{Docker Volume Plugin}
%         {Virtualized the servers using Docker for the test and development environments needs. Implemented docker volume plugin to enable engine deployments to be integrated with external storage systems.}
%         \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeSubheading
        {AI12 Reasoning Challenge}{\textit{February 2020 - April 2020}}
        {Arizona State University}{Tempe, USA}
            \resumeItemListStart
                \item{Research, development, and code implementation of Information Retrieval module and Prediction module.} 
                \item{Implemented code to support GPU inferencing and reduced the prediction time by 1/10th.}
                \item{Performed analysis of failed cases and implemented new methods to increase the accuracy by 15\%.}
                \item{Trained the XLNet Model on the RACE dataset using Google Colab and experimented with new models.}
            \resumeItemListEnd
    \resumeSubheading
        {Question Answering System}{\textit{January 2019 - May 2019}}
        {Zoho Corporation}{Chennai, India}
            \resumeItemListStart
                \item{Built a system to automatically answer FAQs from a set of predefined FAQs stored in PostgreSQL.}
                \item{Designed, developed REST APIs, and communicated with clients to define functional and technical requirements.}
                \item{Designed and configured databases and provided support with maintenance and documentation.}
                \item{This system replaced the monotonous work of support engineers in answering fundamental questions.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
 
\end{document}
